### 2014-03-01 src/paper.Rnw
udpate

\newcommand*\per{\scalebox{.5}{\%}}
\newcommand\Mua{Mutation analysis~}
\newcommand\mua{mutation analysis~}
\begin{comment}
<<setup, include=FALSE, cache=FALSE, message=FALSE, echo=FALSE>>=
clean <- function(x)sub('CONSTRUCTOR','CONSTR',sub('RETURN','R',sub('INCREMENTS','INC',sub('VOID','V',sub('CONDITIONAL','COND',sub('NON','N',sub('VARIABLE','VAR',sub('MEMBER','MEM',sub('DELETE_','D_',sub('REMOVE_','R_',sub('NEGATE_','N_',sub('_CALLS','',sub('EXPERIMENTAL_','E_',x)))))))))))))
#options(warn=-1)
options(digits=3)
opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
render_listings()
logit<-function(x) log(x/(1-x))
require(reshape2)
require(xtable)
require(Mutsel)
@
<<chunk-hook, echo=2>>=
<<setup>>
@
\end{comment}

@@

% 10 pages for the main text + 1 for references.
\section{Introduction}
<<>>=
data(o.pit.all)
data(o.pit.det)
data(r.pit.all)
data(r.pit.det)
@
% 1. Describe the problem
% 2. State your contributions

@@

\subsection{Occurrence of Operators}
\begin{figure*}[t]
<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
o.all <- cbind(projects = rownames(o.pit.all), stack(o.pit.all))
o.all$ind <- clean(o.all$ind)
bcol <- '#2171B5'
#bcol <- 'darkgray'
icol <- '#9ECAE0'
#icol <- 'lightgray'
o.det <- cbind(projects = rownames(o.pit.det), stack(o.pit.det))
o.det$ind <- clean(o.det$ind)
with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F, ylim=c(0,0.6)))
with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))

r.all <- cbind(projects = rownames(r.pit.all), stack(r.pit.all))
r.all$ind <- clean(r.all$ind)
r.det <- cbind(projects = rownames(r.pit.det), stack(r.pit.det))
r.det$ind <- clean(r.det$ind)
with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F,ylim=c(0,0.6)))
with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
@
\caption{Relative fertility of mutation operators. The gray boxes represent detected mutants, while black represents total mutants.}
\label{fig:mfert}

\end{figure*}

% <<prepare,echo=F>>=
% attach(m)
% sdl_f <- mut.avg~sdl.mut.avg + 0
% rnd_f <- mut.avg~lrnd.mut.avg + 0
% 
% sdl_all <- lm(sdl_f)
% rnd_all <- lm(rnd_f)
% 
% sdl_s <- summary(sdl_all)
% rnd_s <- summary(rnd_all)
% 
% sdl.est <- sdl_s$coefficients['sdl.mut.avg','Estimate']
% rnd.est <- rnd_s$coefficients['lrnd.mut.avg','Estimate']
% 
% sdl.r <- sdl_s$r.squared
% rnd.r <- rnd_s$r.squared
% 
% @

>>>>

\newcommand*\per{\scalebox{.5}{\%}}
\newcommand\Mua{Mutation analysis~}
\newcommand\mua{mutation analysis~}
\begin{comment}
<<setup, include=FALSE, cache=FALSE, message=FALSE, echo=FALSE>>=
clean <- function(x)sub('CONSTRUCTOR','CONSTR',sub('RETURN','R',sub('INCREMENTS','INC',sub('VOID','V',sub('CONDITIONAL','COND',sub('NON','N',sub('VARIABLE','VAR',sub('MEMBER','MEM',sub('DELETE_','D_',sub('REMOVE_','R_',sub('NEGATE_','N_',sub('_CALLS','',sub('EXPERIMENTAL_','E_',x)))))))))))))
#options(warn=-1)
options(digits=3)
opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
render_listings()
logit<-function(x) log(x/(1-x))
require(reshape2)
require(xtable)
require(Mutsel)
@
<<chunk-hook, echo=2>>=
<<setup>>
v=data(package='Mutsel')
data(list = v$results[,3])
@
\end{comment}

@@

% 10 pages for the main text + 1 for references.
\section{Introduction}
<<>>=
data(o.dist.all)
data(o.dist.det)
data(r.dist.all)
data(r.dist.det)
@
% 1. Describe the problem
% 2. State your contributions

@@

\subsection{Occurrence of Operators}
\begin{figure*}[t]
<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
o.all$ind <- clean(o.all$ind)
bcol <- '#2171B5'
#bcol <- 'darkgray'
icol <- '#9ECAE0'
#icol <- 'lightgray'
o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
o.det$ind <- clean(o.det$ind)
with(o.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F, ylim=c(0,0.6)))
with(o.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))

r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
r.all$ind <- clean(r.all$ind)
r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
r.det$ind <- clean(r.det$ind)
with(r.det,boxplot(values~ind,horizontal=T,border=c(bcol), col=icol, pch='.', axes=F,ylim=c(0,0.6)))
with(r.all,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
@
\caption{Relative fertility of mutation operators. The blue shade represent detected mutants, while black represents total mutants.}
\label{fig:op}
\end{figure*}

\subsection{SDL vs Random selection}
\begin{figure*}[t]
<<sdl.1,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(mfrow=c(2,2))
with(o.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Original SDL'))
with(o.pit.all, plot(all.cov~x1_per_line.cov, pch='+', main='Original 1 per line'))
with(r.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Randoop SDl'))
with(r.pit.all, plot(all.cov~x1_per_line.cov, pch='+', main='Original 1 per line'))
@
\label{fig:sdl1}
\caption{Statement Deletion vs One per line.}
\end{figure*}
